\documentclass{prgrado}
\usepackage{comment}
\usepackage{ragged2e}
\usepackage{tabularx}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{adjustbox}
\usepackage{rotating}
\usepackage{float}
\usepackage{svg}
\usepackage{multirow}
\usepackage{wrapfig}

\usepackage{pgfplots}
\usepackage{xcolor}
\pgfplotsset{compat=1.18}

\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\setlength{\emergencystretch}{3em}


\title{Análisis de herramientas para la generación automática de historias de usuario y evaluación de las mismas}       

\author{Romina Parada, Gonzalo Caricot Layera, Valentin Dutra y Keiver Fajardo}  

% Fecha de la defensa
\date{\today}                                 
\supervisor{Diego Vallespir}                
\cclicense{by}{4.0}

\hypersetup{
  colorlinks   = true,
  urlcolor     = blue,
  linkcolor    = blue,
  citecolor    = red
}
\usepackage{longtable}
\begin{document}
\setcounter{secnumdepth}{3} 

\frontmatter
\maketitle

\chapter{Agradecimientos}
\input{agradecimientos}
\chapter{Resumen}
\input{resumen}

% índice
\tableofcontents


\mainmatter
\input{introduccion}

% Antecedentes
\chapter{Revisión de antecedentes}
\label{cap:antecedentes}
\input{revision/main}
% Revisión de antecedentes (productos, procesos, publicaciones, etc., tanto a nivel académico como comercial).
% Puede incluir, si es necesario, una breve introducción a los conceptos necesarios para comprender el trabajo.

%El objetivo de este capítulo es presentar la revisión de antecedentes sobre la generación automática de historias de usuario con la utilización de inteligencia artificial. Con este fin, se definieron metodologías tanto para buscar y seleccionar las herramientas, como para analizar las mismas. También se explica el enfoque de análisis aplicado y se muestran los resultados observados, con el fin de evaluar en qué medida cada herramienta cubre los aspectos funcionales definidos para este proyecto.



% parte central
\chapter{Revisión de herramientas}
\label{cap:herramientas}
\input{herramientas/main}

\chapter{Evaluación piloto}
\label{cap:central}
\input{central/main}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Metodología de evaluación de historias de usuario}
\label{cap:evaluacion}
\input{evaluacion/main}

\chapter{Resultados y discusión}
\label{cap:resultados}
\input{resultados/main}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%conclusiones
\chapter{Conclusiones y trabajo futuro}
\label{cap:conclusiones}
\input{conclusiones/main}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Parte final
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{ % inicio backmatter

\backmatter % no numerar capítulos 

% referencias bibliográficas

\newpage
\bibliographystyle{apacite}
\bibliography{referencias}

} % fin backmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% anexos

% --- Anexos (sin numeración y sin secciones internas) ---
\cleardoublepage
\phantomsection
\chapter*{Anexos}
\label{cap:anexo}
\addcontentsline{toc}{chapter}{Anexos}
\markboth{Anexos}{Anexos}

% ===== Anexo 1 =====
\vspace{0.75\baselineskip}
{\large\bfseries Anexo 1 — Prompts y evaluación de herramientas\par}
\vspace{0.25\baselineskip}


Este anexo recopila los \textit{prompts} empleados durante la búsqueda y evaluación de herramientas, con el fin de asegurar la trazabilidad y reproducibilidad del proceso de recolección de información. Se incluyen las consultas realizadas en las plataformas Perplexity y Gemini, así como el registro y control de cambios realizados.

\medskip
\textbf{Perplexity — Prompt utilizado}
\begin{quote}
Estamos realizando un estudio de investigación sistemático en el área de Ingeniería de Software.  
El objetivo es identificar y analizar herramientas existentes que automaticen ciertos aspectos de la ingeniería de requisitos, en particular:  
(a) la generación automática de historias de usuario a partir de documentos/archivos de entrada,  
(b) la validación de la calidad de los requisitos en las historias generadas, y  
(c) la detección de inconsistencias, ambigüedades o duplicidades en los documentos/archivos utilizados como entrada.  

Devuelve únicamente herramientas implementadas y disponibles actualmente (código abierto o comerciales) que puedan probarse de forma práctica. Excluye artículos académicos, propuestas conceptuales o repositorios sin código ejecutable.  

Para cada herramienta válida, incluir:  
- Nombre  
- Enlace oficial o repositorio  
- Canal de uso (CLI, plugin, API, SaaS, paquete, etc.)  
- Enlace de instalación o documentación  
- Fecha o versión del último lanzamiento  
- Tipo de licencia (si es de código abierto)  
- Breve descripción de sus funcionalidades principales  

Considerar únicamente resultados del período 2022–2025.  
Idioma: inglés.  
Fuentes sugeridas: GitHub, GitLab, Bitbucket y marketplaces de software (Atlassian Marketplace, Azure DevOps, JetBrains, etc.).  
Evitar resultados que sean solo artículos o datasets sin ejecutables.  

Proporciona una lista concisa y sin duplicados con las 10 herramientas más relevantes.
\end{quote}

\newpage

\medskip
\textbf{Gemini — Proceso en tres etapas}

\textit{Mensaje 1 — Listado inicial con enlaces oficiales. Objetivo: obtener un conjunto preliminar de herramientas candidatas.}
\par\textbf{Prompt literal}
\begin{quote}
Siguiendo el alcance de la investigación, lista las herramientas implementadas (2022–2025) que puedan probarse de forma práctica y que estén relacionadas con:  
(a) la generación automática de historias de usuario a partir de documentos/archivos de entrada,  
(b) la validación de la calidad de los requisitos en las historias generadas, y  
(c) la detección de inconsistencias, ambigüedades o duplicidades en los documentos/archivos utilizados como entrada.    

Devuelve únicamente el nombre de la herramienta y los enlaces oficiales al producto o repositorio.  
Idioma: inglés. Evita duplicados por nombre o dominio.
\end{quote}

\textit{Mensaje 2 — Refinamiento técnico. Objetivo: obtener detalles técnicos sobre cada herramienta identificada.}
\par\textbf{Prompt literal}
\begin{quote}
Para cada herramienta listada anteriormente, proporciona la siguiente información:  
- Canal de uso (CLI, paquete, plugin de Jira/Azure DevOps/VS Code, SaaS, Docker, API)  
- Enlace a la guía de instalación o documentación (README/docs)  
- Fecha o versión del último lanzamiento y estado de mantenimiento  
- Tipo de licencia (si es de código abierto)  

Devuelve los resultados en formato de tabla Markdown con las columnas:  
\{Nombre | Enlace oficial | Canal de uso | Instalación | Versión/Lanzamiento | Licencia\}.
\end{quote}

\textit{Mensaje 3 — Selección final y verificación rápida. Objetivo: seleccionar las herramientas más relevantes y confirmar que sean ejecutables o factibles de evaluar.}
\par\textbf{Prompt literal}
\begin{quote}
De la tabla anterior, selecciona las 10 herramientas más relevantes (por nombre o dominio) que mejor se ajusten al alcance de la investigación.  
Para cada una, agrega los pasos mínimos de comprobación (por ejemplo, comando de instalación, ejecución en Docker o enlace de registro) que permitan verificar rápidamente su funcionamiento.  

Devuelve una lista breve, clara y directamente accionable.
\end{quote}

\medskip
\textbf{Registro y control de cambios}
\par Durante la búsqueda, se almacenó para cada ejecución la siguiente información:
\begin{itemize}
    \item \textbf{Prompt utilizado}
    \item \textbf{Marca temporal}
    \item \textbf{Modelo de IA empleado} (Gemini o Perplexity)
    \item \textbf{Resultados obtenidos}
\end{itemize}

% ===== Anexo 2 =====
\newpage
\vspace{0.75\baselineskip}
{\large\bfseries Anexo 2\par}
\vspace{0.25\baselineskip}

A continuación se listan, tal como aparecen en las ejecuciones documentadas (sin duplicados; se enumeran todas las ejecuciones por herramienta).

\begin{center}
\begin{longtable}{|
>{\RaggedRight\arraybackslash}p{6.5cm}|
>{\RaggedRight\arraybackslash}p{4cm}|
>{\RaggedRight\arraybackslash}p{3.5cm}|}
\caption{Herramientas de IA, fuente de búsqueda y fecha de ejecución} \\
\hline
\textbf{Herramienta} & \textbf{Motor de búsqueda} & \textbf{Fecha de ejecución} \\
\hline
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continuación}} \\
\hline
\textbf{Herramienta} & \textbf{Motor de búsqueda} & \textbf{Fecha de ejecución} \\
\hline
\endhead

\hline \multicolumn{3}{r}{{Continúa en la siguiente página}} \\
\endfoot

\hline
\endlastfoot

ScopeMaster / Story Analyser for Jira & Perplexity & 22/10/2025 \\
RequirementLinter & Perplexity / Gemini & 22/10/2025 -- 24/10/2025 \\
POPal --- AI Test Case \& User Story Generator for Jira & Perplexity / Gemini & 22/10/2025 -- 24/10/2025 \\
StoryCraft & Perplexity / GitHub & 22/10/2025 -- 24/10/2025 \\
StoryTest (by ScopeMaster) & Perplexity & 22/10/2025 \\
Visual Narrator & Perplexity & 22/10/2025 \\
Featmap & Perplexity & 22/10/2025 \\
USeR (User Story eReviewer) & Perplexity & 22/10/2025 \\
reqSuite RM & Perplexity & 22/10/2025 \\
AQUSA (Automatic Quality User Story Artisan) & Perplexity / Gemini & 22/10/2025 -- 24/10/2025 \\
Modern Requirements4DevOps & Perplexity / Gemini / Marketplace & 22/10/2025 -- 24/10/2025 \\
Copilot4DevOps & Perplexity / Google / Marketplace & 22/10/2025 -- 24/10/2025 \\
Ambiguity Detection Using LLMs (ChaseMcClellan) & Perplexity & 22/10/2025 \\
RE-Ambiguity-Detection-Experiment (+ OpenReq) & Perplexity & 22/10/2025 \\
Reqnroll & Perplexity & 22/10/2025 \\
Curiosity Software --- Quality Modeller & Gemini & 24/10/2025 \\
aqua ALM (AI Copilot) & Gemini / Marketplace & 24/10/2025 \\
GitHub Spec-Kit & Gemini / GitHub & 24/10/2025 \\
AI Requirements Engineer Assistant & Gemini & 24/10/2025 \\
GeneUS & Gemini / Google & 24/10/2025 \\
QVscribe & Gemini & 24/10/2025 \\
Automated User Story Generation with Test Case Specification (GPT-4.0 based) & Gemini & 24/10/2025 \\
StoriesOnBoard & Google & 22/10/2025 -- 24/10/2025 \\
Beam AI User Stories & Google & 22/10/2025 \\
ClickUp & Google & 22/10/2025 -- 24/10/2025 \\
Quanter AI & Google & 24/10/2025 \\
Miro & Google & 24/10/2025 \\
RequirementLinter Public & GitHub & 22/10/2025 -- 24/10/2025 \\
StoryMachine & GitHub & 22/10/2025 -- 24/10/2025 \\
Agile-bot & GitHub & 22/10/2025 -- 24/10/2025 \\
User Story Generator & GitHub & 22/10/2025 -- 24/10/2025 \\
%Story-craft & GitHub & 22/10/2025 -- 24/10/2025 \\
AI-Driven Agile Team & GitHub & 24/10/2025 \\
AutoDev Editor & GitHub & 24/10/2025 \\
Specifai & GitHub & 24/10/2025 \\
StoryBot & GitHub & 24/10/2025 \\
UST - User Story Tutor & GitHub & 24/10/2025 \\
UserStory QE - Agent & Marketplace & 22/10/2025 -- 24/10/2025 \\
QAssert TestCase and UserStory Generator & Marketplace & 22/10/2025 -- 24/10/2025 \\
AI Agile Story / Bug Generation & Marketplace & 22/10/2025 -- 24/10/2025 \\
AI Requirements Copilot for Jira & Marketplace & 22/10/2025 -- 24/10/2025 \\
Storygenie & Marketplace & 22/10/2025 -- 24/10/2025 \\
AutoStory: AI-Powered Ticket Creation for Jira & Marketplace & 24/10/2025 \\
\hline
\end{longtable}
\end{center}


\begin{comment}
    
\begin{longtable}{|p{10cm}|p{5cm}|}
\caption{Herramientas de IA y fuentes de ejecución} \\
\hline
\textbf{Herramienta} & \textbf{Ejecuciones} \\
\hline
\endfirsthead

\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continuación}} \\
\hline
\textbf{Herramienta} & \textbf{Ejecuciones} \\
\hline
\endhead

\hline \multicolumn{2}{r}{{Continúa en siguiente página}} \\
\endfoot

\hline
\endlastfoot

ScopeMaster / Story Analyser for Jira & Perplexity 01, Gemini 03 \\
RequirementLinter & Perplexity 01, Gemini 01, Gemini 02 \\
POPal --- AI Test Case \& User Story Generator for Jira & Perplexity 01, Gemini 01 \\
StoryCraft & Perplexity 01, Perplexity 02 \\
StoryTest (by ScopeMaster) & Perplexity 01 \\
Visual Narrator & Perplexity 01 \\
Featmap & Perplexity 01 \\
USeR (User Story eReviewer) & Perplexity 01 \\
reqSuite RM & Perplexity 01 \\
AQUSA (Automatic Quality User Story Artisan) & Perplexity 01, Gemini 03 \\
Kollabe User Story Generator & Perplexity 02 \\
Easy-Peasy AI --- User Story Generator & Perplexity 02 \\
Modern Requirements4DevOps & Perplexity 02, Gemini 03 \\
Copilot4DevOps & Perplexity 02 \\
rmToo & Perplexity 02 \\
Ambiguity Detection Using LLMs (ChaseMcClellan) & Perplexity 02 \\
ambiguity\_detection & Perplexity 02 \\
RE-Ambiguity-Detection-Experiment (+ OpenReq) & Perplexity 02 \\
Reqnroll & Perplexity 02 \\
Curiosity Software --- Quality Modeller & Gemini 01 \\
aqua ALM (AI Copilot) & Gemini 01, Gemini 03 \\
GitHub Spec-Kit & Gemini 02 \\
LLM Azure Function App & Gemini 02 \\
AI Requirements Engineer Assistant & Gemini 02 \\
GeneUS & Gemini 02 \\
aqua (Declarative CLI Version Manager) & Gemini 03 \\
QVscribe & Gemini 03 \\
GenAI-Enabled Backlog Grooming (Prototype) & Gemini 03 \\
Automated User Story Generation with Test Case Specification (GPT-4.0 based) & Gemini 03 \\
MyAgileCopilot --- ChatGPT for Product Backlog & Gemini 03 \\
AI User Story \& Test Case Generator for Jira & Gemini 03 \\
TestRay --- Requirements \& Test Management for Jira & Gemini 03 \\
AI Test Case Generator for Azure (bakeqa) & Gemini 03 \\
Aqua & Google 02 \\
Get Generative AI & Google 02 \\
Inflectra & Google 02 \\
|
Beam AI User Stories & Google 01 \\
Intelligent User Story Assistan & Google 01 \\
ClickUp & Google 01, Google 02 \\
StoriesOnBoard & Google 01, Google 02 \\
Quanter AI & Google 02 \\
Miro & Google 02 \\
RequirementLinter Public & Github 01 \\
TraceVibe & Github 01 \\
StoryCraft - Professional User Story Generator & Github 01 \\
Agile-bot & Github 01, Github 02 \\
StoryMachine & Github 01, Github 02 \\
Cursor rules for Agile & Github 01, Github 02 \\
Copilot4DevOps & Google 01, Google 02 \\
User Story Generator & Github 01, Github 02\\
Story-craft & Github 01, Github 02\\
AI-Driven Agile Team & Github 02 \\
AutoDev Editor & Github 02 \\
Multiagent-Prioritization & Github 02 \\
Spec Kit & Github 02 \\
Specifai & Github 02 \\
StoryBot & Github 02 \\
UST - User Story Tutor & Github 02 \\
Vibe Coder MCP Server & Github 02 \\
3 AI Amigos: Multi-Agent Product Development Team & Github 02 \\
UserStory QE - Agent & Marketplace 01 \\
QAssert TestCase and UserStory Generator & Marketplace 01 \\
AI Agile Story / Bug Generation & Marketplace 01 \\
AI Issue Breakdown Assistant for Jira (Cloud and Private AI) & Marketplace 01 \\
AI Issues Automator for Jira & Marketplace 01 \\
CirrusInsightsNow.AI & Marketplace 01 \\
DevGenius & Marketplace 01 \\
Qlerify Software Modeler & Marketplace 01 \\
Agile User Story Map, Portfolio Roadmaps and Persona for Jira & Marketplace 01 \\
AI Test Case and User Story Issue Auto Generator for Jira & Marketplace 01, Marketplace 02 \\
AI User Story and Test Case Generator for Jira & Marketplace 01, Marketplace 02 \\
AI Assistant Extension for Azure DevOps & Marketplace 01, Marketplace 02 \\
AI Requirements Copilot for Jira & Marketplace 01, Marketplace 02 \\
Storygenie & Marketplace 01, Marketplace 02 \\
AI Test Case Generator & Marketplace 02 \\
Story Analyser & Marketplace 02 \\
AutoStory: AI-Powered Ticket Creation for Jira & Marketplace 02 \\


\hline
\end{longtable}
\end{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ===== Anexo 3 =====
\newpage
\vspace{0.75\baselineskip}
{\large\bfseries Anexo 3\par}
\vspace{0.25\baselineskip}

Este anexo contiene las historias de usuario esperadas construidas por nosotros, en la Tabla \ref{tab:historias_esperadas}, junto a sus criterios de aceptación en la Tabla \ref{tab:criterios_esperados}.

Las funcionalidades esperadas también fueron construidas por nosotros, están presentes en la tabla \ref{tab:funcionalidedes_esperadas}.

\begin{longtable}{|c|p{12cm}|}
\caption{Historias de Usuario Esperadas} \label{tab:historias_esperadas} \\
\hline
\textbf{Referencia} & \textbf{Historia de usuario} \\
\hline
\endfirsthead

\caption{Historias de Usuario Esperadas - Continuación} \\
\hline
\textbf{Referencia} & \textbf{Historia de usuario} \\
\hline
\endhead

\hline
\endfoot

\hline
\endlastfoot

HUE1 & As administrative staff, I want to register a new patient's data to enroll them in the system. \\ \hline
HUE2 & As the system, I want to generate a unique patient number to identify each record. \\ \hline
HUE3 & As administrative staff, I want to edit a registered patient's data to keep the information up to date. \\ \hline
HUE4 & As administrative staff, I want to register a patient's medical background in their electronic clinical record to understand their health status. \\ \hline
HUE5 & As administrative staff, I want to search for a patient by their name to access their information. \\ \hline
HUE6 & As administrative staff, I want to search for a patient by their identity document to retrieve their record. \\ \hline
HUE7 & As administrative staff, I want to search for a patient by their patient number to retrieve their record. \\ \hline
HUE8 & As a doctor, I want to search for a patient by their name to consult their clinical record. \\ \hline
HUE9 & As a doctor, I want to search for a patient by their identity document to access their clinical record. \\ \hline
HUE10 & As a doctor, I want to search for a patient by their patient number to access their clinical record. \\ \hline
HUE11 & As administrative staff, I want to view a patient's complete information to consult their personal data. \\ \hline
HUE12 & As administrative staff, I want to view a patient's scheduled appointments to consult their information. \\ \hline
HUE13 & As administrative staff, I want to register an appointment to schedule a patient's medical care. \\ \hline
HUE14 & As administrative staff, I want to cancel an existing appointment to free up the time slot in the schedule. \\ \hline
HUE15 & As administrative staff, I want to edit an existing appointment to change its date without losing the information. \\ \hline
HUE16 & As a patient, I want to be notified by email when my appointment is modified so I stay informed. \\ \hline
HUE17 & As a patient, I want to be notified by text message to my phone number when my appointment is modified so I stay informed. \\ \hline
HUE18 & As a doctor, I want to access a patient's clinical record to review their prior information. \\ \hline
HUE19 & As a doctor, I want to register the diagnosis made during the appointment to document the medical care provided. \\ \hline
HUE20 & As a patient, I want to consult my electronic clinical record to access my medical information. \\ \hline
HUE21 & As administrative staff, I want to register doctors with their respective specialties to enroll them in the system. \\ \hline
HUE22 & As administrative staff, I want to define a doctor's attention hours to enable appointment assignment. \\ \hline
HUE23 & As administrative staff, I want to edit a registered doctor's data to keep the information up to date. \\ \hline
HUE24 & As administrative staff, I want to edit a doctor's attention hours to keep the information up to date. \\ \hline
HUE25 & As administrative staff, I want to deactivate a registered doctor to keep the information up to date. \\ \hline
HUE26 & As administrative staff, I want to activate a registered doctor to keep the information up to date. \\ \hline
HUE27 & As the system, I want to define system roles to organize access to functionalities. \\ \hline
HUE28 & As the system, I want to associate permissions with each role to control access to system functionalities. \\ \hline
HUE29 & As administrative staff, I want to generate an invoice associated with an appointment to have a payment receipt. \\ \hline
HUE30 & As the system, I want to generate a unique identifier to identify each invoice. \\ \hline
HUE31 & As a pharmacist, I want to generate an invoice associated with a medication to have a payment receipt. \\ \hline
HUE32 & As a pharmacist, I want to search for a patient by their identity document to consult the patient's medications. \\ \hline
HUE33 & As a pharmacist, I want to view a patient's medications to consult their medications. \\ \hline
HUE34 & As administrative staff, I want to generate an invoice associated with a medication to have a payment receipt. \\ \hline
HUE35 & As administrative staff, I want to view a patient's medications to consult their medications. \\ \hline
HUE36 & As a patient, I want to receive an email notification with the invoice attached to access the payment receipt. \\ \hline
HUE37 & As a patient, I want to be notified by text message to my phone number with the invoice information to stay informed about the charge. \\ \hline
HUE38 & As a pharmacist, I want to register medications to keep the hospital inventory up to date. \\ \hline
HUE39 & As a pharmacist, I want to register supplies to keep the hospital inventory up to date. \\ \hline
HUE40 & As a pharmacist, I want to edit how many medications are available to keep the hospital inventory up to date. \\ \hline
HUE41 & As a pharmacist, I want to edit how many supplies are available to keep the hospital inventory up to date. \\ \hline
HUE42 & As a pharmacist, I want to associate a medication with the patient who collected it so the system generates the corresponding invoice. \\ \hline
HUE43 & As a pharmacist, I want to consult the medication inventory sorted by available quantity. \\ \hline
HUE44 & As a pharmacist, I want to consult the medication inventory sorted by expiration date. \\ \hline
HUE45 & As a pharmacist, I want to consult the supply inventory sorted by available quantity. \\ \hline
HUE46 & As a pharmacist, I want to consult the supply inventory sorted by expiration date. \\ \hline
HUE47 & As a pharmacist, I want to check how many units of a medication are available to make timely decisions. \\ \hline
HUE48 & As a pharmacist, I want to check how many units of a supply are available to make timely decisions. \\ \hline
HUE49 & As a pharmacist, I want to search for a medication by its name to access its information. \\ \hline
HUE50 & As a pharmacist, I want to search for a supply by its name to access its information. \\ \hline
HUE51 & As a pharmacist, I want to know when a medication is about to expire to make timely decisions. \\ \hline
HUE52 & As a pharmacist, I want to know when a supply is about to expire to make timely decisions. \\ \hline
HUE53 & As a pharmacist, I want to know when a medication has a low number of available units to make timely decisions. \\ \hline
HUE54 & As a pharmacist, I want to know when a supply has a low number of available units to make timely decisions. \\ \hline
HUE55 & As an analyst, I want to view appointment statistics by specialty to evaluate the workload. \\ \hline
HUE56 & As an analyst, I want to view financial reports of the services to evaluate the hospital's income and economic performance. \\ \hline
HUE57 & As an analyst, I want to view supply consumption to evaluate the hospital's inventory usage. \\ \hline
\end{longtable}

\begin{longtable}{|c|c|p{9cm}|}
\caption{Criterios de aceptación Esperados} 
\label{tab:criterios_esperados} \\
\hline
\textbf{Referencia CAE} & \textbf{Ref. HUE} & \textbf{Criterio de aceptación} \\
\hline
\endfirsthead

\caption{Criterios de aceptación Esperados - Continuación} \\
\hline
\textbf{Referencia CAE} & \textbf{Ref. HUE} & \textbf{Criterio de aceptación} \\
\hline
\endhead

\hline
\endfoot

\hline
\endlastfoot
ACE1.1 & HUE1 & The system must request the full name, date of birth, sex, identity document, and contact details (email address and phone number). \\ \hline
ACE1.2 & HUE1 & The system must display an error if a patient with the entered identity document already exists. \\ \hline
ACE1.3 & HUE1 & The system must assign a unique patient number to the new patient. \\ \hline

ACE3.1 & HUE3 & The system must allow modifying the full name, date of birth, sex, identity document, and contact details (email address and phone number). \\ \hline

ACE4.1 & HUE4 & The system must allow entering the patient's blood type. \\ \hline
ACE4.2 & HUE4 & The system must allow entering chronic diseases, allergies, relevant injuries, and regular medications along with the date they started/occurred, with the option to indicate "from birth". \\ \hline

ACE5.1 & HUE5 & The system must display a search field that allows entering the name. \\ \hline
ACE5.2 & HUE5 & The system must display a list of patients whose names match the entered data. \\ \hline

ACE6.1 & HUE6 & The system must display a search field that allows entering the identity document. \\ \hline
ACE6.2 & HUE6 & The system must display a list of patients whose documents match the entered data. \\ \hline

ACE7.1 & HUE7 & The system must display a search field that allows entering the patient number. \\ \hline
ACE7.2 & HUE7 & The system must display a list of patients whose patient numbers match the entered data. \\ \hline

ACE8.1 & HUE8 & The system must display a search field that allows entering the name. \\ \hline
ACE8.2 & HUE8 & The system must display a list of patients whose names match the entered data. \\ \hline

ACE9.1 & HUE9 & The system must display a search field that allows entering the identity document. \\ \hline
ACE9.2 & HUE9 & The system must display a list of patients whose documents match the entered data. \\ \hline

ACE10.1 & HUE10 & The system must have a search field that allows searching by patient number. \\ \hline
ACE10.2 & HUE10 & The system must display a list of patients whose patient numbers match the entered data. \\ \hline

ACE11.1 & HUE11 & The system must display the patient's personal data: full name, date of birth, sex, identity document, and contact details (email address and phone number). \\ \hline
ACE11.2 & HUE11 & The system must display the patient number. \\ \hline

ACE12.1 & HUE12 & The system must display the appointment details: specialty, doctor, schedule, and status. \\ \hline

ACE13.1 & HUE13 & The system must allow selecting the specialty and doctor for the appointment. \\ \hline
ACE13.2 & HUE13 & The system must display the available time slots in the selected doctor's schedule. \\ \hline
ACE13.3 & HUE13 & The system must display an error if an appointment already exists at that time slot. \\ \hline
ACE13.4 & HUE13 & The system must change the appointment status to "Confirmed" after a successful registration. \\ \hline

ACE14.1 & HUE14 & The system must allow changing the appointment status to "Canceled". \\ \hline
ACE14.2 & HUE14 & The system must make the previous time slot available again in the doctor's schedule. \\ \hline

ACE15.1 & HUE15 & The system must allow editing the date and time of an existing appointment. \\ \hline
ACE15.2 & HUE15 & The system must validate that the new time slot is available. \\ \hline

ACE16.1 & HUE16 & The system must indicate in the notification if the appointment was canceled. \\ \hline
ACE16.2 & HUE16 & The system must indicate in the notification if the appointment had a schedule change. \\ \hline
ACE16.3 & HUE16 & The system must include the new appointment date in the notification when a date change occurs. \\ \hline

ACE17.1 & HUE17 & The system must indicate in the notification if the appointment was canceled. \\ \hline
ACE17.2 & HUE17 & The system must indicate in the notification if the appointment had a schedule change. \\ \hline
ACE17.3 & HUE17 & The system must include the new appointment date in the notification when a date change occurs. \\ \hline

ACE18.1 & HUE18 & The system must allow access to the clinical record only to users with the doctor role. \\ \hline
ACE18.2 & HUE18 & The system must list the diagnoses for each appointment confirmed by the patient. \\ \hline
ACE18.3 & HUE18 & The system must display the patient's medical background. \\ \hline

ACE19.1 & HUE19 & The system must include the date, name, and specialty of the responsible doctor in each record. \\ \hline
ACE19.2 & HUE19 & The system must allow marking the appointment as Attended when a diagnosis is registered. \\ \hline
ACE19.3 & HUE19 & The system must allow marking the appointment as Not attended. \\ \hline
ACE19.4 & HUE19 & The system must prevent registering a diagnosis when the appointment is marked as Not attended. \\ \hline

ACE20.1 & HUE20 & The system must list all appointments associated with the patient. \\ \hline
ACE20.2 & HUE20 & The system must list all medications associated with the patient. \\ \hline
ACE20.3 & HUE20 & The system must list all invoices associated with the patient. \\ \hline
ACE20.4 & HUE20 & The system must allow sorting the information by date, responsible doctor, or specialty. \\ \hline
ACE20.5 & HUE20 & The system must allow viewing the details of each listed item. \\ \hline
ACE21.1 & HUE21 & The system must allow registering the doctor's full name, identity document number, and contact details (email address and phone number). \\ \hline
ACE21.2 & HUE21 & The system must allow associating a specialty with the doctor being registered. \\ \hline
ACE21.3 & HUE21 & The system must allow defining the doctor's status as active or inactive. \\ \hline
ACE21.4 & HUE21 & The doctor's name and identity document cannot be left empty in the registration. \\ \hline

ACE22.1 & HUE22 & The system must allow defining the start time and end time per day of the week. \\ \hline
ACE22.2 & HUE22 & The system must allow defining more than one time slot per day. \\ \hline
ACE22.3 & HUE22 & The system must display an error if the time slots for the same day overlap. \\ \hline
ACE22.4 & HUE22 & The system must display an error if the start times precede the end times. \\ \hline

ACE23.1 & HUE23 & The system must allow editing the doctor's full name, identity document number, and contact details. \\ \hline

ACE24.1 & HUE24 & The system must allow editing the days of the week for attention. \\ \hline
ACE24.2 & HUE24 & The system must allow editing the start time and end time for a day of the week. \\ \hline
ACE24.3 & HUE24 & The system must display an error if the time slots for the same day overlap. \\ \hline
ACE24.4 & HUE24 & The system must display an error if the start times precede the end times. \\ \hline

ACE25.1 & HUE25 & The system must allow changing the doctor's status to inactive. \\ \hline
ACE26.1 & HUE26 & The system must allow changing the doctor's status to active. \\ \hline

ACE27.1 & HUE27 & The system must define the following roles: administrative staff, doctor, pharmacist, analyst, and patient. \\ \hline

ACE28.1 & HUE28 & The system must associate functionalities with each role. \\ \hline
ACE28.2 & HUE28 & The system must display an error if a user accesses a functionality not defined in their role. \\ \hline

ACE29.1 & HUE29 & The system must include in the invoice the patient's full name, appointment specialty, date, and total cost. \\ \hline
ACE29.2 & HUE29 & The system must include a unique identifier in the invoice. \\ \hline
ACE29.3 & HUE29 & The system must associate the invoice with the patient and the appointment. \\ \hline

ACE31.1 & HUE31 & The system must include in the invoice the patient's full name, medication name, date, and total cost. \\ \hline
ACE31.2 & HUE31 & The system must include a unique identifier in the invoice. \\ \hline
ACE31.3 & HUE31 & The systedatem must associate the invoice with the patient and the medication. \\ \hline

ACE32.1 & HUE32 & The system must have a search field that allows searching by identity document. \\ \hline
ACE32.2 & HUE32 & The system must display a list of results matching the entered data. \\ \hline

ACE33.1 & HUE33 & The system must list the patient's medications. \\ \hline
ACE33.2 & HUE33 & The system must allow generating the invoice. \\ \hline

ACE34.1 & HUE34 & The system must include in the invoice the patient's full name, medication name, date, and total cost. \\ \hline
ACE34.2 & HUE34 & The system must include a unique identifier in the invoice. \\ \hline
ACE34.3 & HUE34 & The system must associate the invoice with the patient and the medication. \\ \hline

ACE35.1 & HUE35 & The system must list the patient's medications. \\ \hline
ACE35.2 & HUE35 & The system must allow generating the invoice. \\ \hline

ACE36.1 & HUE36 & The system must send an email to the patient's email address containing: invoice identifier, patient name, date, and service type (appointment or medication). \\ \hline
ACE36.2 & HUE36 & The system must include in the subject line that it is a hospital invoice. \\ \hline
ACE36.3 & HUE36 & The system must include the invoice attached in PDF format. \\ \hline
ACE36.4 & HUE36 & The system must send the email within 10 minutes after the invoice is generated. \\ \hline

ACE37.1 & HUE37 & The system must send a text message to the patient's phone number containing: invoice identifier, patient name, date, and service type (appointment or medication). \\ \hline
ACE37.2 & HUE37 & The system must include the total cost of the invoice. \\ \hline
ACE37.3 & HUE37 & The system must send the text message within 10 minutes after the invoice is generated. \\ \hline

ACE38.1 & HUE38 & The system must register each medication with name, manufacturer, available units, stock number, and expiration date. \\ \hline
ACE38.2 & HUE38 & The system must display an error if the expiration date is earlier than the current date. \\ \hline
ACE38.3 & HUE38 & The system must display an error if the stock number is not unique. \\ \hline
ACE38.4 & HUE38 & The system must display an error if the medication name is left empty. \\ \hline
ACE38.5 & HUE38 & The system must display an error if the number of available units is less than 0. \\ \hline

ACE39.1 & HUE39 & The system must register each supply with name, manufacturer, available units, stock number, and expiration date. \\ \hline
ACE39.2 & HUE39 & The system must display an error if the expiration date is less than or equal to the current date. \\ \hline
ACE39.3 & HUE39 & The system must display an error if the stock number already exists in the system. \\ \hline
ACE39.4 & HUE39 & The system must display an error if the supply name is left empty. \\ \hline
ACE39.5 & HUE39 & The system must display an error if the number of available units is less than 0. \\ \hline

ACE40.1 & HUE40 & The system must allow modifying the available units. \\ \hline
ACE40.2 & HUE40 & The system must display an error if the number of available units is less than 0. \\ \hline

ACE41.1 & HUE41 & The system must allow modifying the available units. \\ \hline
ACE41.2 & HUE41 & The system must display an error if the number of available units is less than 0. \\ \hline

ACE42.1 & HUE42 & The system must associate the collected medication with the patient. \\ \hline
ACE42.2 & HUE42 & The system must allow selecting the quantity to collect. \\ \hline
ACE42.3 & HUE42 & The system must update the available units according to the collected quantity. \\ \hline
ACE42.4 & HUE42 & The system must display an error if the collected quantity exceeds the available units. \\ \hline

ACE43.1 & HUE43 & The system must display the medication name and the number of available units. \\ \hline
ACE43.2 & HUE43 & The system sorts from lowest to highest. \\ \hline

ACE44.1 & HUE44 & The system must display the medication name and the expiration date. \\ \hline
ACE44.2 & HUE44 & The system sorts from lowest to highest. \\ \hline

ACE45.1 & HUE45 & The system must display the supply name and the number of available units. \\ \hline
ACE45.2 & HUE45 & The system sorts from lowest to highest. \\ \hline

ACE46.1 & HUE46 & The system must display the supply name and the expiration date. \\ \hline
ACE46.2 & HUE46 & The system sorts from lowest to highest. \\ \hline

ACE47.1 & HUE47 & The system must display the number of available units of the medication. \\ \hline
ACE48.1 & HUE48 & The system must display the number of available units of the supply. \\ \hline

ACE49.1 & HUE49 & The system must have a search field that allows searching by medication name. \\ \hline
ACE49.2 & HUE49 & The system must display a list of medications whose names match the entered data. \\ \hline

ACE50.1 & HUE50 & The system must have a search field that allows searching by supply name. \\ \hline
ACE50.2 & HUE50 & The system must display a list of supplies whose names match the entered data. \\ \hline

ACE51.1 & HUE51 & The system must allow listing all medications and sorting them by expiration date. \\ \hline
ACE51.2 & HUE51 & The system must display the medication's expiration date. \\ \hline
ACE51.3 & HUE51 & The system must highlight in red when one month remains before the medication expires. \\ \hline

ACE52.1 & HUE52 & The system must allow listing all supplies and sorting them by expiration date. \\ \hline
ACE52.2 & HUE52 & The system must display the supply's expiration date. \\ \hline
ACE52.3 & HUE52 & The system must highlight in red when one month remains before the supply expires. \\ \hline

ACE53.1 & HUE53 & The system must allow listing all medications and sorting them by available units. \\ \hline
ACE53.2 & HUE53 & The system must display the number of available units of the medication. \\ \hline
ACE53.3 & HUE53 & The system must highlight in red when fewer than 10 units remain. \\ \hline

ACE54.1 & HUE54 & The system must allow listing all supplies and sorting them by available units. \\ \hline
ACE54.2 & HUE54 & The system must display the number of available units of the supply. \\ \hline
ACE54.3 & HUE54 & The system must highlight in red when fewer than 10 units remain. \\ \hline

ACE55.1 & HUE55 & The system must list all existing specialties. \\ \hline
ACE55.2 & HUE55 & The system must allow choosing a specialty. \\ \hline
ACE55.3 & HUE55 & The system must display the total number of appointments: overall, attended, canceled, confirmed, and not attended. \\ \hline
ACE55.4 & HUE55 & The system must allow choosing a date range. \\ \hline
ACE55.5 & HUE55 & The system must display an error if the start date is later than the end date. \\ \hline
ACE55.6 & HUE55 & The system must display an error if the end date is later than the current date. \\ \hline

ACE56.1 & HUE56 & The system must display the hospital's total income. \\ \hline
ACE56.2 & HUE56 & The system must display the income by specialty. \\ \hline
ACE56.3 & HUE56 & The system must display the income by medication. \\ \hline
ACE56.4 & HUE56 & The system must allow choosing the query date range. \\ \hline
ACE56.5 & HUE56 & The system must display an error if the start date is later than the end date. \\ \hline
ACE56.6 & HUE56 & The system must display an error if the end date is later than the current date. \\ \hline

ACE57.1 & HUE57 & The system must allow filtering by name. \\ \hline
ACE57.2 & HUE57 & The system must list all supplies sorted by consumption (number of units collected). \\ \hline
ACE57.3 & HUE57 & The system must display the total number of units collected. \\ \hline
ACE57.4 & HUE57 & The system must allow choosing the query date range. \\ \hline
ACE57.5 & HUE57 & The system must display an error if the start date is later than the end date. \\ \hline
ACE57.6 & HUE57 & The system must display an error if the end date is later than the current date. \\ \hline
\end{longtable}

\begin{longtable}{|c|l|p{9cm}|}
\caption{Funcionalidades del sistema por categoría.}
\label{tab:funcionalidades} \\
\hline
\textbf{Ref.} & \textbf{Categoría} & \textbf{Funcionalidad} \\
\hline
\endfirsthead
\hline
\textbf{Ref.} & \textbf{Categoría} & \textbf{Funcionalidad} \\
\hline
\endhead

F1 & Pacientes & Register patients with personal and medical data \\ \hline
F2 & Pacientes & Assign a unique identifier to each patient \\ \hline
F3 & Pacientes & Modify patient personal and contact information \\ \hline
F4 & Pacientes & Record patient medical background such as allergies or chronic diseases \\ \hline
F5 & Pacientes & Search patients by name, identity document or identifier \\ \hline
F6 & Pacientes & View complete patient information \\ \hline
F7 & Pacientes & Access patient personal and clinical information \\ \hline
F8 & Turnos & Create medical appointments linking patient, specialty and doctor \\ \hline
F9 & Turnos & View availability of registered doctors \\ \hline
F10 & Turnos & Prevent overlapping medical appointments \\ \hline
F11 & Turnos & Modify appointment date and time \\ \hline
F12 & Turnos & Cancel existing appointments \\ \hline
F13 & Turnos & Notify patients when appointments are modified or canceled \\ \hline
F14 & Turnos & Manage appointment lifecycle and status \\ \hline
F15 & Turnos & Track appointment states such as confirmed, canceled or attended \\ \hline
F16 & Historia Clínica & Register diagnoses, treatments and clinical progress \\ \hline
F17 & Historia Clínica & Edit electronic clinical records \\ \hline
F18 & Historia Clínica & Associate a date with each clinical record entry \\ \hline
F19 & Historia Clínica & Store patient medical and clinical information \\ \hline
F20 & Historia Clínica & Restrict access to clinical information to authorized users \\ \hline
F21 & Historia Clínica & Allow doctors to access and review patient clinical history \\ \hline
F22 & Historia Clínica & Allow patients to consult their electronic clinical record \\ \hline
F23 & Historia Clínica & Secure management of electronic medical records \\ \hline
F24 & Personal & Register medical professionals with personal information \\ \hline
F25 & Personal & Associate medical specialties with professionals \\ \hline
F26 & Personal & Manage medical professional information \\ \hline
F27 & Personal & Define and modify doctor attention hours \\ \hline
F28 & Personal & Activate or deactivate medical professionals for scheduling \\ \hline
F29 & Personal & Manage healthcare staff availability \\ \hline
F30 & Personal & Manage user roles and access permissions \\ \hline
F31 & Personal & Validate permissions before performing system actions \\ \hline
F32 & Facturación & Generate electronic invoices for medical consultations \\ \hline
F33 & Facturación & Generate invoices for medication delivery \\ \hline
F34 & Facturación & Associate invoices with patients and medical services \\ \hline
F35 & Facturación & Assign a unique identifier to each invoice \\ \hline
F36 & Facturación & Send automatic notifications when invoices are generated \\ \hline
F37 & Facturación & Attach digital invoices to patient notifications \\ \hline
F38 & Facturación & Manage billing related to healthcare services \\ \hline
F39 & Facturación & Store financial documents and proof of payment \\ \hline
F40 & Inventario & Register medications and medical supplies in the system \\ \hline
F41 & Inventario & Store stock levels and expiration dates of medications \\ \hline
F42 & Inventario & Update inventory stock when medication deliveries are recorded \\ \hline
F43 & Inventario & Detect minimum stock levels in the inventory \\ \hline
F44 & Inventario & Notify when medications or supplies are about to expire \\ \hline
F45 & Inventario & Consult inventory sorted by quantity or expiration date \\ \hline
F46 & Inventario & Track pharmacy inventory and supplies availability \\ \hline
F47 & Inventario & Manage medication and supplies stock control \\ \hline
F48 & Reportes & Generate statistical reports for healthcare data \\ \hline
F49 & Reportes & Generate financial reports of hospital income \\ \hline
F50 & Reportes & Report number of consultations by medical specialty \\ \hline
F51 & Reportes & Report appointment status statistics \\ \hline
F52 & Reportes & Report medication and supplies consumption \\ \hline
F53 & Reportes & Filter reports using date ranges \\ \hline
F54 & Reportes & Analyze system usage and healthcare metrics \\ \hline

\end{longtable}




% ===== Anexo 4 =====
\newpage
\vspace{0.75\baselineskip}
{\large\bfseries Anexo 4\par}
\vspace{0.25\baselineskip}

En la tabla \ref{tab:alignment_histories} se muestra la alineación de historias generadas y las tres historias esperadas correspondientes, aquellas que tienen la mayor similitud semántica.

\begin{longtable}{|c|c|c|}
\caption{Alineación de historias generadas y las tres correspondientes historias esperadas, aquellas que tienen la mayor similitud semántica.}
\label{tab:alignment_histories} \\
\hline
\textbf{Ref. Historia Generada} & \textbf{Top-3 Ref. Historia Esperada} & \textbf{Similitud} \\
\hline
\endfirsthead

\hline
\textbf{Ref. Historia Generada} & \textbf{Top-3 Ref. Historia Esperada} & \textbf{Similitud Semántica} \\
\hline
\endhead

HU1 & HUE1 | HUE4 | HUE13 & 0.8612 | 0.8227 | 0.7280 \\ \hline
HU2 & HUE3 | HUE23 | HUE24 & 0.8599 | 0.8337 | 0.6954 \\ \hline
HU3 & HUE7 | HUE6 | HUE5 & 0.8921 | 0.8908 | 0.8800 \\ \hline
HU4 & HUE11 | HUE12 | HUE18 & 0.8349 | 0.6402 | 0.6389 \\ \hline
HU5 & HUE13 | HUE22 | HUE21 & 0.7197 | 0.7018 | 0.6890 \\ \hline
HU6 & HUE21 | HUE12 | HUE55 & 0.6867 | 0.6610 | 0.6383 \\ \hline
HU7 & HUE14 | HUE15 | HUE24 & 0.8235 | 0.8067 | 0.6964 \\ \hline
HU8 & HUE16 | HUE17 | HUE12 & 0.9096 | 0.8544 | 0.6655 \\ \hline
HU9 & HUE13 | HUE12 | HUE22 & 0.7575 | 0.7293 | 0.6764 \\ \hline
HU10 & HUE4 | HUE19 | HUE20 & 0.8207 | 0.7201 | 0.6893 \\ \hline
HU11 & HUE20 | HUE4 | HUE18 & 0.9514 | 0.8082 | 0.7764 \\ \hline
HU12 & HUE21 | HUE26 | HUE1 & 0.8332 | 0.7226 | 0.7187 \\ \hline
HU13 & HUE22 | HUE24 | HUE13 & 0.8282 | 0.7965 | 0.6766 \\ \hline
HU14 & HUE27 | HUE28 | HUE24 & 0.7749 | 0.7596 | 0.2863 \\ \hline
HU15 & HUE34 | HUE29 | HUE31 & 0.8436 | 0.8177 | 0.7646 \\ \hline
HU16 & HUE37 | HUE36 | HUE34 & 0.7938 | 0.7842 | 0.6950 \\ \hline
HU17 & HUE39 | HUE38 | HUE44 & 0.8840 | 0.8820 | 0.7716 \\ \hline
HU18 & HUE38 | HUE39 | HUE40 & 0.6956 | 0.6826 | 0.6626 \\ \hline
HU19 & HUE46 | HUE52 | HUE44 & 0.7368 | 0.7102 | 0.7092 \\ \hline
HU20 & HUE46 | HUE45 | HUE43 & 0.8704 | 0.8611 | 0.8601 \\ \hline
HU21 & HUE56 | HUE55 | HUE57 & 0.6356 | 0.6126 | 0.5485 \\ \hline
HU22 & HUE46 | HUE44 | HUE51 & 0.3132 | 0.3044 | 0.2991 \\ \hline
HU23 & HUE16 | HUE52 | HUE17 & 0.4149 | 0.3442 | 0.3435 \\ \hline
\end{longtable}


En la tabla \ref{tab:alignment_criteria} se muestra la alineación de criterios generadas y los correspondientes criterios esperados, aquellos que tienen la mayor similitud semántica.

\begin{longtable}{|c|p{5cm}|p{4cm}|}
\caption{Alineación de criterios generadas y los correspondientes criterios esperados, ordenados por similitud semántica.}
\label{tab:alignment_criteria} \\
\hline
\textbf{Ref. Criterio Generado} & \textbf{Ref. Criterio Esperado} & \textbf{Similitud Semántica} \\
\hline
\endfirsthead

\hline
\textbf{Ref. Criterio Generado} & \textbf{Ref. Criterio Esperado} & \textbf{Similitud Semántica} \\
\hline
\endhead

CA1.1 & CAE1.1 | CAE1.3 | CAE1.2 & 0.6461 | 0.5010 | 0.4869 \\ \hline
CA1.2 & CAE1.3 | CAE1.2 | CAE1.1 & 0.8034 | 0.6005 | 0.3620 \\ \hline
CA1.3 & CAE1.2 | CAE1.1 | CAE1.3 & 0.6793 | 0.3826 | 0.3798 \\ \hline
CA2.1 & CAE3.1 & 0.5844 \\ \hline
CA3.1 & CAE7.1 | CAE7.2 & 0.5183 | 0.3361 \\ \hline
CA4.1 & CAE11.1 | CAE11.2 & 0.6495 | 0.6465 \\ \hline
CA5.1 & CAE13.1 | CAE13.2 | CAE13.3 | CAE13.4 & 0.8839 | 0.6539 | 0.3365 | 0.3328 \\ \hline
CA5.2 & CAE13.3 | CAE13.2 | CAE13.4 | CAE13.1 & 0.6867 | 0.4883 | 0.4527 | 0.4379 \\ \hline
CA6.1 & CAE21.3 | CAE21.1 | CAE21.2 | CAE21.4 & 0.6052 | 0.5617 | 0.5123 | 0.3819 \\ \hline
CA7.1 & CAE14.1 | CAE14.2 & 0.7505 | 0.5071 \\ \hline
CA7.2 & CAE14.2 | CAE14.1 & 0.4651 | 0.2897 \\ \hline
CA8.1 & CAE16.2 | CAE16.3 | CAE16.1 & 0.5508 | 0.5235 | 0.3510 \\ \hline
CA9.1 & CAE13.4 | CAE13.3 | CAE13.2 | CAE13.1 & 0.6186 | 0.4562 | 0.4211 | 0.3850 \\ \hline
CA10.1 & CAE4.1 | CAE4.2 & 0.5540 | 0.5336 \\ \hline
CA10.2 & CAE4.2 | CAE4.1 & 0.2781 | 0.0750 \\ \hline
CA11.1 & CAE20.1 | CAE20.4 | CAE20.3 | CAE20.5 | CAE20.2 & 0.3505 | 0.3038 | 0.2838 | 0.2621 | 0.2312 \\ \hline
CA11.2 & CAE20.5 | CAE20.1 | CAE20.4 | CAE20.2 | CAE20.3 & 0.1461 | 0.0590 | 0.0338 | 0.0246 | 0.0215 \\ \hline
CA12.1 & CAE21.1 | CAE21.2 | CAE21.3 | CAE21.4 & 0.5073 | 0.4369 | 0.4153 | 0.3070 \\ \hline
CA13.1 & CAE22.1 | CAE22.2 | CAE22.3 | CAE22.4 & 0.6306 | 0.5931 | 0.4899 | 0.3994 \\ \hline
CA13.2 & CAE22.2 | CAE22.1 | CAE22.3 | CAE22.4 & 0.4138 | 0.3740 | 0.3236 | 0.1917 \\ \hline
CA14.1 & CAE27.1 & 0.4571 \\ \hline
CA14.2 & CAE27.1 & 0.1423 \\ \hline
CA15.1 & CAE34.2 | CAE34.3 | CAE34.1 & 0.8195 | 0.5923 | 0.5358 \\ \hline
CA15.2 & CAE34.3 | CAE34.1 | CAE34.2 & 0.7850 | 0.7180 | 0.5914 \\ \hline
CA16.1 & CAE37.3 | CAE37.1 | CAE37.2 & 0.4679 | 0.4064 | 0.2654 \\ \hline
CA17.1 & CAE39.1 | CAE39.3 | CAE39.2 | CAE39.5 | CAE39.4 & 0.6501 | 0.3412 | 0.3248 | 0.2788 | 0.2680 \\ \hline
CA18.1 & CAE38.3 | CAE38.1 | CAE38.2 | CAE38.5 | CAE38.4 & 0.3703 | 0.2418 | 0.1769 | 0.1501 | 0.1286 \\ \hline
CA19.1 & CAE46.1 | CAE46.2 & 0.5553 | 0.3143 \\ \hline
CA20.1 & CAE46.1 | CAE46.2 & 0.5525 | 0.4330 \\ \hline
CA21.1 & CAE56.1 | CAE56.2 | CAE56.3 | CAE56.4 | CAE56.5 | CAE56.6 & 0.2759 | 0.2710 | 0.2352 | 0.2059 | 0.1022 | 0.0927 \\ \hline
CA21.2 & CAE56.4 | CAE56.5 | CAE56.6 | CAE56.3 | CAE56.2 | CAE56.1 & 0.6086 | 0.3515 | 0.3312 | 0.2378 | 0.2327 | 0.1424 \\ \hline
\end{longtable}

En la tabla \ref{tab:fun_historias_esperadas} se muestra la similitud de las funcionalidades con las historias esperadas.

\begin{longtable}{|c|c|c|}
\caption{Similitud semántica entre funcionalidades e historias de usuario esperadas} 
\label{tab:fun_historias_esperadas}\\
\hline
\textbf{Ref. Funcionalidad} & \textbf{Top-3 Ref. Historia Esperada} & \textbf{Similitud} \\
\hline
\endhead

F0 & HU1 | HU4 | HU13 & 0.7888 | 0.6946 | 0.5996 \\ \hline
F1 & HU2 | HU42 | HU30 & 0.7433 | 0.5912 | 0.5842 \\ \hline
F2 & HU3 | HU23 | HU24 & 0.7452 | 0.7276 | 0.6199 \\ \hline
F3 & HU4 | HU18 | HU19 & 0.7273 | 0.6530 | 0.6052 \\ \hline
F4 & HU9 | HU6 | HU32 & 0.8525 | 0.8451 | 0.8041 \\ \hline
F5 & HU11 | HU18 | HU4 & 0.8006 | 0.6583 | 0.6132 \\ \hline
F6 & HU11 | HU18 | HU20 & 0.8231 | 0.7849 | 0.7251 \\ \hline
F7 & HU13 | HU12 | HU22 & 0.6395 | 0.6264 | 0.6245 \\ \hline
F8 & HU21 | HU26 | HU25 & 0.7009 | 0.6708 | 0.5526 \\ \hline
F9 & HU13 | HU22 | HU12 & 0.5447 | 0.5275 | 0.4956 \\ \hline
F10 & HU15 | HU14 | HU24 & 0.7862 | 0.6505 | 0.6366 \\ \hline
F11 & HU14 | HU15 | HU25 & 0.7836 | 0.5554 | 0.4248 \\ \hline
F12 & HU16 | HU17 | HU24 & 0.7814 | 0.6827 | 0.5782 \\ \hline
F13 & HU13 | HU12 | HU22 & 0.5664 | 0.5619 | 0.5389 \\ \hline
F14 & HU12 | HU19 | HU13 & 0.5837 | 0.5073 | 0.4818 \\ \hline
F15 & HU19 | HU4 | HU1 & 0.6261 | 0.5658 | 0.5102 \\ \hline
F16 & HU3 | HU23 | HU4 & 0.7746 | 0.7552 | 0.7376 \\ \hline
F17 & HU4 | HU18 | HU1 & 0.6244 | 0.5570 | 0.5554 \\ \hline
F18 & HU4 | HU11 | HU18 & 0.6792 | 0.6441 | 0.6065 \\ \hline
F19 & HU11 | HU18 | HU35 & 0.6304 | 0.6253 | 0.5777 \\ \hline
F20 & HU18 | HU11 | HU4 & 0.7562 | 0.6503 | 0.6372 \\ \hline
F21 & HU20 | HU4 | HU18 & 0.8195 | 0.7300 | 0.6964 \\ \hline
F22 & HU4 | HU20 | HU3 & 0.5893 | 0.5740 | 0.5371 \\ \hline
F23 & HU21 | HU26 | HU1 & 0.6785 | 0.6721 | 0.6568 \\ \hline
F24 & HU21 | HU26 | HU22 & 0.6219 | 0.4619 | 0.4167 \\ \hline
F25 & HU23 | HU21 | HU11 & 0.6523 | 0.6359 | 0.6187 \\ \hline
F26 & HU22 | HU24 | HU13 & 0.8408 | 0.7258 | 0.4943 \\ \hline
F27 & HU25 | HU26 | HU22 & 0.6416 | 0.6402 | 0.5984 \\ \hline
F28 & HU22 | HU13 | HU26 & 0.5568 | 0.5540 | 0.5109 \\ \hline
F29 & HU28 | HU27 | HU23 & 0.6892 | 0.6069 | 0.2454 \\ \hline
F30 & HU28 | HU27 | HU13 & 0.4926 | 0.4164 | 0.1241 \\ \hline
F31 & HU34 | HU29 | HU31 & 0.7735 | 0.7493 | 0.7308 \\ \hline
F32 & HU34 | HU31 | HU29 & 0.8305 | 0.8126 | 0.6821 \\ \hline
F33 & HU34 | HU42 | HU31 & 0.6675 | 0.6531 | 0.6421 \\ \hline
F34 & HU30 | HU34 | HU31 & 0.8485 | 0.5443 | 0.5422 \\ \hline
F35 & HU36 | HU29 | HU37 & 0.6035 | 0.5589 | 0.5412 \\ \hline
F36 & HU36 | HU37 | HU34 & 0.7147 | 0.6556 | 0.6166 \\ \hline
F37 & HU13 | HU37 | HU34 & 0.5113 | 0.4706 | 0.4430 \\ \hline
F38 & HU34 | HU29 | HU31 & 0.3208 | 0.3149 | 0.3120 \\ \hline
F39 & HU39 | HU38 | HU40 & 0.8391 | 0.8059 | 0.6603 \\ \hline
F40 & HU46 | HU44 | HU43 & 0.7599 | 0.7587 | 0.6809 \\ \hline
F41 & HU40 | HU41 | HU39 & 0.6062 | 0.6001 | 0.5965 \\ \hline
F42 & HU45 | HU43 | HU46 & 0.5937 | 0.5475 | 0.4593 \\ \hline
F43 & HU52 | HU51 | HU44 & 0.7852 | 0.7676 | 0.6943 \\ \hline
F44 & HU46 | HU45 | HU43 & 0.7853 | 0.7512 | 0.7319 \\ \hline
F45 & HU46 | HU39 | HU45 & 0.7469 | 0.7378 | 0.7339 \\ \hline
F46 & HU39 | HU41 | HU43 & 0.7159 | 0.6860 | 0.6750 \\ \hline
F47 & HU4 | HU56 | HU55 & 0.4612 | 0.4593 | 0.4508 \\ \hline
F48 & HU56 | HU57 | HU34 & 0.7436 | 0.5082 | 0.4741 \\ \hline
F49 & HU55 | HU21 | HU19 & 0.6585 | 0.5598 | 0.5315 \\ \hline
F50 & HU55 | HU12 | HU22 & 0.7143 | 0.5949 | 0.5291 \\ \hline
F51 & HU39 | HU47 | HU41 & 0.6220 | 0.6135 | 0.5854 \\ \hline
F52 & HU44 | HU46 | HU56 & 0.2918 | 0.2838 | 0.2625 \\ \hline
F53 & HU57 | HU1 | HU56 & 0.5130 | 0.4477 | 0.4460 \\ \hline

\end{longtable}

En la tabla \ref{tab:fun_historias_generadas} se muestra la similitud de las funcionalidades con las historias generadas.

\begin{longtable}{|c|c|c|}
\caption{Similitud semántica entre funcionalidades e historias de usuario generadas} 
\label{tab:fun_historias_generadas}\\
\hline
\textbf{Ref. Funcionalidad} & \textbf{Top-3 Ref. Historia Generada} & \textbf{Similitud} \\
\hline
\endhead

F1  & H1 | H4 | H13 & 0.7888 | 0.6946 | 0.5996 \\ \hline
F2  & H2 | H42 | H30 & 0.7433 | 0.5912 | 0.5842 \\ \hline
F3  & H3 | H23 | H24 & 0.7452 | 0.7276 | 0.6199 \\ \hline
F4  & H4 | H18 | H19 & 0.7273 | 0.6530 | 0.6052 \\ \hline
F5  & H9 | H6 | H32 & 0.8525 | 0.8451 | 0.8041 \\ \hline
F6  & H11 | H18 | H4 & 0.8006 | 0.6583 | 0.6132 \\ \hline
F7  & H11 | H18 | H20 & 0.8231 | 0.7849 | 0.7251 \\ \hline
F8  & H13 | H12 | H22 & 0.6395 | 0.6264 | 0.6245 \\ \hline
F9  & H21 | H26 | H25 & 0.7009 | 0.6708 | 0.5526 \\ \hline
F10 & H13 | H22 | H12 & 0.5447 | 0.5275 | 0.4956 \\ \hline
F11 & H15 | H14 | H24 & 0.7862 | 0.6505 | 0.6366 \\ \hline
F12 & H14 | H15 | H25 & 0.7836 | 0.5554 | 0.4248 \\ \hline
F13 & H16 | H17 | H24 & 0.7814 | 0.6827 | 0.5782 \\ \hline
F14 & H13 | H12 | H22 & 0.5664 | 0.5619 | 0.5389 \\ \hline
F15 & H12 | H19 | H13 & 0.5837 | 0.5073 | 0.4818 \\ \hline
F16 & H19 | H4 | H1 & 0.6261 | 0.5658 | 0.5102 \\ \hline
F17 & H3 | H23 | H4 & 0.7746 | 0.7552 | 0.7376 \\ \hline
F18 & H4 | H18 | H1 & 0.6244 | 0.5570 | 0.5554 \\ \hline
F19 & H4 | H11 | H18 & 0.6792 | 0.6441 | 0.6065 \\ \hline
F20 & H11 | H18 | H35 & 0.6304 | 0.6253 | 0.5777 \\ \hline
F21 & H18 | H11 | H4 & 0.7562 | 0.6503 | 0.6372 \\ \hline
F22 & H20 | H4 | H18 & 0.8195 | 0.7300 | 0.6964 \\ \hline
F23 & H4 | H20 | H3 & 0.5893 | 0.5740 | 0.5371 \\ \hline
F24 & H21 | H26 | H1 & 0.6785 | 0.6721 | 0.6568 \\ \hline
F25 & H21 | H26 | H22 & 0.6219 | 0.4619 | 0.4167 \\ \hline
F26 & H23 | H21 | H11 & 0.6523 | 0.6359 | 0.6187 \\ \hline
F27 & H22 | H24 | H13 & 0.8408 | 0.7258 | 0.4943 \\ \hline
F28 & H25 | H26 | H22 & 0.6416 | 0.6402 | 0.5984 \\ \hline
F29 & H22 | H13 | H26 & 0.5568 | 0.5540 | 0.5109 \\ \hline
F30 & H28 | H27 | H23 & 0.6892 | 0.6069 | 0.2454 \\ \hline
F31 & H28 | H27 | H13 & 0.4926 | 0.4164 | 0.1241 \\ \hline
F32 & H34 | H29 | H31 & 0.7735 | 0.7493 | 0.7308 \\ \hline
F33 & H34 | H31 | H29 & 0.8305 | 0.8126 | 0.6821 \\ \hline
F34 & H34 | H42 | H31 & 0.6675 | 0.6531 | 0.6421 \\ \hline
F35 & H30 | H34 | H31 & 0.8485 | 0.5443 | 0.5422 \\ \hline
F36 & H36 | H29 | H37 & 0.6035 | 0.5589 | 0.5412 \\ \hline
F37 & H36 | H37 | H34 & 0.7147 | 0.6556 | 0.6166 \\ \hline
F38 & H13 | H37 | H34 & 0.5113 | 0.4706 | 0.4430 \\ \hline
F39 & H34 | H29 | H31 & 0.3208 | 0.3149 | 0.3120 \\ \hline
F40 & H39 | H38 | H40 & 0.8391 | 0.8059 | 0.6603 \\ \hline
F41 & H46 | H44 | H43 & 0.7599 | 0.7587 | 0.6809 \\ \hline
F42 & H40 | H41 | H39 & 0.6062 | 0.6001 | 0.5965 \\ \hline
F43 & H45 | H43 | H46 & 0.5937 | 0.5475 | 0.4593 \\ \hline
F44 & H52 | H51 | H44 & 0.7852 | 0.7676 | 0.6943 \\ \hline
F45 & H20 | H17 | H19 & 0.8543 | 0.5867 | 0.5061 \\ \hline
F46 & H17 | H20 | H18 & 0.7492 | 0.6896 | 0.6693 \\ \hline
F47 & H17 | H18 | H20 & 0.6975 | 0.6330 | 0.6301 \\ \hline
F48 & H21 | H1 | H10 & 0.6544 | 0.4800 | 0.4630 \\ \hline
F49 & H21 | H15 | H9 & 0.6935 | 0.4681 | 0.4528 \\ \hline
F50 & H21 | H6 | H5 & 0.6128 | 0.5854 | 0.5601 \\ \hline
F51 & H9 | H21 | H6 & 0.7141 | 0.5938 | 0.5869 \\ \hline
F52 & H17 | H21 | H20 & 0.5796 | 0.5030 | 0.4753 \\ \hline
F53 & H21 | H22 | H20 & 0.5679 | 0.3972 | 0.2637 \\ \hline
F54 & H21 | H1 | H10 & 0.5076 | 0.4582 | 0.4342 \\ \hline
\end{longtable}

\end{document}
